CrypTool Script\footnote{ Background reading for the CrypTool program}\\ Mathematics and Cryptography

### 2003-05-20 script/de/chapters/primes.tex
be update numbertheory and overfull hbox fixes

{\bf Annahme:} \quad Es gibt {\em endlich} viele Primzahlen.
\\*[4pt] {\bf Schluss:} \quad Dann lassen sie sich auflisten $p_1
< p_2 < p_3 < \dots < p_n$, wobei $n$ f"ur die (endliche) Anzahl
der Primzahlen steht. $p_n$ w"are also die gr"o"ste Primzahl. Nun
betrachtet Euklid die Zahl $a = p_1 \cdot p_2 \cdots p_n +1$.
Diese Zahl kann keine Primzahl sein, da sie in unserer
Primzahlenliste nicht auftaucht. Also muss sie durch eine Primzahl
teilbar sein. D.h. es gibt eine nat"urliche Zahl $i$ zwischen $1$
und $n$, so dass $p_i$ die Zahl $a$ teilt. Nat"urlich teilt $p_i$
auch das Produkt $a-1 = p_1 \cdot p_2 \cdots p_n$, da $p_i$ ja ein
Faktor von $a-1$ ist. Da $ p_i $ die Zahlen $ a $ und $ a-1 $
teilt, teilt sie auch die Differenz dieser Zahlen. Daraus folgt:
$p_i$ teilt  $a - (a-1) = 1$. $p_i$ m"usste also $1$ teilen und
das ist unm"oglich.\\*[4pt] 
{\bf Widerspruch}: \quad Unsere Annahme war falsch.\par
Also gibt es {\em unendlich} viele Primzahlen
\hyperlink{primhfk}{(siehe "Ubersicht unter \ref{s:primhfk} "uber die
Anzahl von Primzahlen in verschiedenen Intervallen).}\par \vskip + 10pt

@@

Zur Zeit sind die 4 gr"o"sten bekannten Primzahlen auch Mersenne-Primzahlen.
Erst die 5.-gr"o"ste bekannte Primzahl hat eine andere Form: sie geh"ort 
zu den sogenannten \hyperlink{generalizedFermatprimes}{verallgemeinerten 
Fermat-Primzahlen}.

@@

    Innerhalb des Projektes ''Distributed Search for Fermat Number Dividers'',
    das von Leonid Durman angeboten wird, gibt es ebenfalls Fortschritte 
    beim Finden von neuen Primzahl-Riesen
    ({\href{http://www.fermatsearch.org/}
       {\tt http://www.fermatsearch.org/}}  --  diese Webseite hat 
    Verkn"upfungen zu Seiten in russisch, italienisch und deutsch).
    \begin{sloppypar}
    Die entdeckten Faktoren k"onnen sowohl zusammengesetzte nat"ur"-liche als auch 
    prime nat"urliche Zahlen sein.
    \end{sloppypar}

>>>>

{\bf Annahme:} \quad Es gibt {\em endlich} viele Primzahlen.
\\*[4pt] {\bf Schluss:} \quad Dann lassen sie sich auflisten $p_1
< p_2 < p_3 < \dots < p_n$, wobei $n$ f"ur die (endliche) Anzahl
der Primzahlen steht. $p_n$ w"are also die gr"o"ste Primzahl. Nun
betrachtet Euklid die Zahl $a = p_1 \cdot p_2 \cdots p_n +1$.
Diese Zahl kann keine Primzahl sein, da sie in unserer
Primzahlenliste nicht auftaucht. Also muss sie durch eine Primzahl
teilbar sein. D.h. es gibt eine nat"urliche Zahl $i$ zwischen $1$
und $n$, so dass $p_i$ die Zahl $a$ teilt. Nat"urlich teilt $p_i$
auch das Produkt $a-1 = p_1 \cdot p_2 \cdots p_n$, da $p_i$ ja ein
Faktor von $a-1$ ist. Da $ p_i $ die Zahlen $ a $ und $ a-1 $
teilt, teilt sie auch die Differenz dieser Zahlen. Daraus folgt:
$p_i$ teilt  $a - (a-1) = 1$. $p_i$ m"usste also $1$ teilen und
das ist unm"oglich.\\*[4pt] 
{\bf Widerspruch}: \quad Unsere Annahme war falsch.\par
Also gibt es {\em unendlich} viele Primzahlen
(siehe \hyperlink{primhfk}{"Ubersicht unter \ref{s:primhfk}} "uber die
Anzahl von Primzahlen in verschiedenen Intervallen).\par \vskip + 10pt

@@

Zur Zeit sind die 4 gr"o"sten bekannten Primzahlen auch Mersenne-Primzahlen.
Erst die 5.-gr"o"ste bekannte Primzahl hat eine andere Form: sie geh"ort 
zu den sogenannten verallgemeinerten Fermat-Primzahlen (siehe
\hyperlink{generalizedFermatprimes}{unten in}
Kapitel~\ref{spezialzahlentypen}).

@@

    Innerhalb des Projektes ``Distributed Search for Fermat Number Dividers'',
    das von Leonid Durman angeboten wird, gibt es ebenfalls Fortschritte 
    beim Finden von neuen Primzahl-Riesen
    ({\href{http://www.fermatsearch.org/}
       {\tt http://www.fermatsearch.org/}}  --  diese Webseite hat 
    Verkn"upfungen zu Seiten in russisch, italienisch und deutsch).
    \begin{sloppypar}
    Die entdeckten Faktoren k"onnen sowohl zusammengesetzte nat"ur"-liche als auch 
    prime nat"urliche Zahlen sein.
    \end{sloppypar}

### 2003-05-20 script/en/chapters/moderncryptography.tex
be update numbertheory and overfull hbox fixes

If we know the various prime factors $ p_1, \dots , p_k $ of $ N, $ then $ \phi 
(N) = N \cdot (1-\frac{1}{p_1}) \,
\cdots \, (1-\frac{1}{p_k}) $\footnote{Further formulas for the Euler phi function are in the 
article \hyperlink{Kap_3_8}{Introduction to Elementary Number Theory with Examples, chapter 3.8}.}.

>>>>

If we know the various prime factors $ p_1, \dots , p_k $ of $ N, $ then $ \phi 
(N) = N \cdot (1-\frac{1}{p_1}) \,
\cdots \, (1-\frac{1}{p_k}) $\footnote{Further formulas for the Euler phi
function are in the article ``Introduction to Elementary Number Theory with
Examples'', chapter~\ref{patternsandstructures}.}.

### 2003-05-20 script/en/chapters/numbertheory.tex
be update numbertheory and overfull hbox fixes

\newpage
%\hypertarget{Kap_3}
\section{Introduction to Elementary Number Theory with Examples}
(Bernhard Esslinger, besslinger@web.de, July 2001, Updates: Dec. 2001, June 2002, Feb. 2003) \\

@@

% --------------------------------------------------------------------------
\vskip +10pt
\subsubsection{Fast calculation of high powers} \hypertarget{hohpot}{} \label{hohpot}\index{Power}
%\subsubsection*{3.6.3.1 ~~~Fast calculation of high powers} \hypertarget{hohpot}{} \index{Power}
%\addcontentsline{toc}{subsubsection}{~~~~~~~~~~3.6.3.1 ~Fast calculation of high powers}
RSA encryption and decryption\footnote{See \hyperlink{Kapitel_3_10}{chapter 3.10 Proof of the RSA procedure with Euler-Fermat} \index{RSA}
and \hyperlink{Kapitel_3_12}{chapter 3.13 The RSA procedure with actual numbers}.} entails calculating high powers modulo $m$. 
For example, the calculation ($100^5) {\rm ~(mod~} 3)$ exceeds the 32-bit long integer\index{Long integer} number range provided we calculate $a^n$ 
by actually multiplying a with itself $n$ times in line with the definition. In the case of extremely large numbers, even 
a fast computer chip would take longer than the age of the universe to calculate a single exponential. Luckily, there is 
an extremely effective shortcut for calculating exponentials (but not for calculating logarithms).

@@

The unique inverse is an essential condition for cryptography (see Section 3.10: \hyperlink{RSABeweis}{Proof of the RSA procedure with Euler-Fermat}).

@@

% --------------------------------------------------------------------------
\subsubsection{Patterns and structures}
\hypertarget{Kap_3_8}{}

@@

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Proof of the RSA procedure with Euler-Fermat}
\hypertarget{Kapitel_3_10}{}\index{RSA}

@@

\vspace{4ex}
\begin{center}
\fbox{\parbox{15cm}{
    \emph{Hermann Hesse\footnotemark:}\\
    To let the possible happen, you again and again have to try the impossible.
}}
\end{center}
\addtocounter{footnote}{0}\footnotetext{%
  German/Swiss writer and Nobel Prize winner, July 2, 1877 $-$ August 9, 1962.}
% --------------------------------------------------------------------------
\subsubsection{Status regarding factorisation of concrete large numbers}
\label{NoteFactorisation}

The web page
\href{http://www.crypto-world.com}{\texttt{http://www.crypto-world.com}}\ 
contains an excellent overview about the factoring 
records\index{Factorisation!factoring records} of composed
integers using different methods.
\hypertarget{C158-chap3}{}
The current record (as of June 2002) obtained using the GNFS method
(General Number Field Sieve) factorised a 158-digit into its both prime
factors (these are build with 73 and 86 decimal digits).

This record, established on January 18, 2002 by researchers of the German
University of Bonn\footnote{%
\href{http://www.ercim.org/publication/Ercim\_News/enw49/franke.html, 2002-01}
{\texttt{http://www.ercim.org/publication/Ercim\_News/enw49/franke.html, 2002-01}}}, got much less attention within the press than the
solution of the RSA challenge\footnote{\href{http://www.rsasecurity.com/rsalabs/challenges/factoring/numbers.html}
         {\texttt{http://www.rsasecurity.com/rsalabs/challenges/factoring/numbers.html}}}, established on August 22, 1999, when
researchers from the Netherlands factorised the 155-digit number into its
both 78-digit primes (see chapter \ref{chptSecurityParam}). 
One reason is that 512 bit RSA-155 was a kind of {\em magic} border.

@@

\begin{minipage}{\textwidth}
\vspace{3ex}
Links:
\vspace{-10pt}
\begin{itemize}
\item[]   \href{http://www.loria.fr/~zimmerma/records/gnfs158}{\texttt{http://www.loria.fr/~zimmerma/records/gnfs158}} \\
          \href{http://www.crypto-world.com/FactorRecords.html}{\texttt{http://www.crypto-world.com/FactorRecords.html}} \\
          \href{http://www.crypto-world.com/announcements/c158.txt}{\texttt{http://www.crypto-world.com/announcements/c158.txt}}
\end{itemize}
\end{minipage}
\vspace{12pt}

As you notice the factorised compound numbers built of 2 prime factors are
much smaller than the especially structured numbers, for which primality 
tests\index{Primality testing} are able to decide whether they are prime 
or not (see chapters 2.4 and 2.5).

@@

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{The RSA procedure with actual numbers}\hypertarget{Kapitel_3_12}{}
\index{RSA}

@@

% --------------------------------------------------------------------------
\subsubsection{RSA with slightly larger primes and a text of upper case letters}

@@

% --------------------------------------------------------------------------
\subsubsection{ RSA with slightly more larger primes and a text made up of ASCII characters}

@@

{\bf Comments:} \\
The original message consisted of a sentence containing $31$ characters (coded with the \hyperlink{Grossbuchstaben-Alphabet}{capital letters alphabet}
\index{Capital letters alphabet} from section 3.12.2). 
Each group of $16$ decimal numbers is then combined to form one number (the last number is filled with zeros). These 
numbers are raised to the power of $e$.

@@

\bibitem[GISA2002]{GISA2002} \index{GISA 2002}
    GISA (German Information Security Agency) \\
    {\em Recommendation for key length selection}, Bonn, Sep. 2002, \\
    \href{http://www.bsi.bund.de/esig/basics/techbas/krypto/bund02v7.pdf}
    {\tt http://www.bsi.bund.de/esig/basics/techbas/krypto/bund02v7.pdf} \\
    A statement on these recommendations: \\
    \href{http://www.secorvo.de/publikat/stellungnahme-algorithmenempfehlung-020307.pdf}
    {\texttt{http://www.secorvo.de/publikat/\\
    \vspace*{1cm}stellungnahme-algorithmenempfehlung-020307.pdf}}

@@

   \item Factorisation records and challenges \index{Factorisation!factorisation records}\\
         \href{http://www.crypto-world.com/}
         {\texttt{http://www.crypto-world.com/}} \\
         \href{http://www.uni-bonn.de/Aktuelles/Pressemitteilungen/pm02/pm035-02.html}
         {\texttt{http://www.uni-bonn.de/Aktuelles/Pressemitteilungen/pm02/pm035-02.html}} \\
         \href{http://www.ercim.org/publication/Ercim\_News/enw49/franke.html, 2002-01}
         {\texttt{http://www.ercim.org/publication/Ercim\_News/enw49/franke.html, 2002-01}} \\
         \href{http://www.rsasecurity.com/rsalabs/challenges/factoring/numbers.html}
         {\texttt{http://www.rsasecurity.com/rsalabs/challenges/factoring/numbers.html}}

@@

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\newpage
\subsection*{Appendix A: the greatest common divisor (gcd) of whole numbers and the two
Algorithms of Euclid} \hypertarget{Appendix_A}{}
\addcontentsline{toc}{subsection}{Appendix A: the greatest common divisor (gcd) of whole numbers and the two
Algorithms of Euclid}\index{Euclidean algorithm!extended}\index{Gcd}

@@

This section list the source code of the RSA examples in section
\hyperlink{Kapitel_3_12}{``The RSA procedure with actual numbers''} using
Mathematica and Pari-GP syntax.

>>>>

\newpage
%\hypertarget{Kap_3}
\section{Introduction to Elementary Number Theory with Examples}
(Bernhard Esslinger, besslinger@web.de, July 2001, Updates: Dec. 2001, June 2002, May 2003) \\

@@

% --------------------------------------------------------------------------
\vskip +10pt
\subsubsection{Fast calculation of high powers} \hypertarget{hohpot}{} \label{hohpot}\index{Power}
%\subsubsection*{3.6.3.1 ~~~Fast calculation of high powers} \hypertarget{hohpot}{} \index{Power}
%\addcontentsline{toc}{subsubsection}{~~~~~~~~~~3.6.3.1 ~Fast calculation of high powers}
RSA encryption and decryption\footnote{See chapter \ref{rsaproof} (Proof of the
RSA procedure with Euler-Fermat) \index{RSA} and chapter~\ref{rsaconcrete} (The
RSA procedure with actual numbers).} entails calculating high powers modulo
$m$.  For example, the calculation ($100^5) {\rm ~(mod~} 3)$ exceeds the 32-bit
long integer\index{Long integer} number range provided we calculate $a^n$ by
actually multiplying a with itself $n$ times in line with the definition. In
the case of extremely large numbers, even a fast computer chip would take
longer than the age of the universe to calculate a single exponential. Luckily,
there is an extremely effective shortcut for calculating exponentials (but not
for calculating logarithms).

@@

The unique inverse is an essential condition for cryptography (see section~\ref{rsaproof}).

@@

% --------------------------------------------------------------------------
\subsubsection{Patterns and structures}
\hypertarget{Kap_3_8}{}\label{patternsandstructures}

@@

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Proof of the RSA procedure with Euler-Fermat}
\hypertarget{Kapitel_3_10}{}\index{RSA}\label{rsaproof}

@@

\vspace{4ex}
\begin{center}
\fbox{\parbox{15cm}{
    \emph{Hermann Hesse\footnotemark:}\\
    To let the possible happen, you again and again have to try the impossible.
}}
\end{center}
\addtocounter{footnote}{0}\footnotetext{%
  German/Swiss writer and Nobel Prize winner, July 2, 1877 $-$ August 9, 1962.}

% --------------------------------------------------------------------------
\subsubsection{Status regarding factorisation of concrete large numbers}
\label{NoteFactorisation}

The web page
\href{http://www.crypto-world.com}{\texttt{http://www.crypto-world.com}}\ 
contains an excellent overview about the factoring 
records\index{Factorisation!factoring records} of composed
integers using different methods.

The current record (as of May 2003) obtained using the GNFS method
(General Number Field Sieve) factorised a 160-digit into its both prime
factors (these are build with each 80 decimal digits).

The last records with factorisation algorithms for general numbers are:

% --------------------------------------------------------------------------
\vskip +20pt
\paragraph{RSA-155} \label{RSA-155} \index{RSA-155}\mbox{}

On August 22, 1999 researchers from the Netherlands found the solution of the
RSA challenge\footnote{\href{http://www.rsasecurity.com/rsalabs/challenges/factoring/numbers.html}
         {\texttt{http://www.rsasecurity.com/rsalabs/challenges/factoring/numbers.html}}}. They factorised a 155-digit number into its both 78-digit primes
(see chapter \ref{chptSecurityParam}).

This 512 bit RSA-155 meant to reach a kind of {\em magic} border.

% --------------------------------------------------------------------------
\vskip +20pt
\paragraph{C158} \label{C158} \index{C158}\mbox{}
\hypertarget{C158-chap3}{}

On January 18, 2002 researchers of the German University of Bonn\footnote{%
\href{http://www.ercim.org/publication/Ercim\_News/enw49/franke.html, 2002-01}
{\texttt{http://www.ercim.org/publication/Ercim\_News/enw49/franke.html, 2002-01}}}
factorised a 158-digit number into its both prime factors (these are build
with 73 and 86 decimal digits) using the GNFS method (General Number Field
Sieve).

This record got much less attention within the press than the solution of
RSA-155.

@@

\begin{minipage}{\textwidth}
\vspace{3ex}
Links:
\vspace{-10pt}
\begin{itemize}
\item[]   \href{http://www.loria.fr/~zimmerma/records/gnfs158}
       {\texttt{http://www.loria.fr/~zimmerma/records/gnfs158}} \\
          \href{http://www.crypto-world.com/FactorRecords.html}
       {\texttt{http://www.crypto-world.com/FactorRecords.html}} \\
          \href{http://www.crypto-world.com/announcements/c158.txt}
       {\texttt{http://www.crypto-world.com/announcements/c158.txt}}
\end{itemize}
\end{minipage}
\vspace{12pt}

% --------------------------------------------------------------------------
\vskip +20pt
\paragraph{RSA-160} \label{RSA-160} \index{RSA-160}\mbox{}

On January 18, 2002 researchers of the German University of Bonn\footnote{%
   \href{http://www.loria.fr/~zimmerma/records/rsa160}
{\texttt{http://www.loria.fr/~zimmerma/records/rsa160}}} 
factorised a 160-digit number into its both prime factors (these are build
with each 80 decimal digits) using the GNFS method (General Number Field
Sieve).

The  computations for the factorization of RSA160 took place at the 
German Information Security Agency (GISA) in Bonn\footnote{%
Every year the GISA\index{GISA} creates a paper to describe which 
crypto algorithms are feasible to generate digital signatures according
to the German signature law -- under participation of experts from
economy and science. To review signature methods based on the
factorisation problem the GISA also co-operates with researchers of the
University of Bonn.
Further information about crypto algorithms on the web page of GISA:
   \href{http://www.bsi.bund.de/esig/basics/techbas/krypto/index.htm}
{\texttt{http://www.bsi.bund.de/esig/basics/techbas/krypto/index.htm}}.
}.

-----------
The composite number called ``RSA-160'' is (the following 3 lines contain
one number):
$$
\begin{array}{c}
215274110271888970189601520131282542925777358884567598017049 \\
767677813314521885913567301105977349105960249790711158521430 \\
2079314665202840140619946994927570407753
\end{array}
$$
The factorisation of RSA-160 resulted in the following two prime factors:
$$
\begin{array}{c}
p = 45427892858481394071686190649738831 \\         
    656137145778469793250959984709250004157335359
\end{array}
$$
and
$$
\begin{array}{c}
q = 47388090603832016196633832303788951 \\
    973268922921040957944741354648812028493909367
\end{array}
$$

The calculations took place between December 2002 and April 2003.

\begin{minipage}{\textwidth}
\vspace{3ex}
Links:
\vspace{-10pt}
\begin{itemize}
\item[]   \href{http://www.loria.fr/~zimmerma/records/rsa160}
       {\texttt{http://www.loria.fr/~zimmerma/records/rsa160}} \\
          \href{http://www.loria.fr/~zimmerma/records/factor.html}
       {\texttt{http://www.loria.fr/~zimmerma/records/factor.html}} \\
          \href{http://www.crypto-world.com/FactorWorld.html}
       {\texttt{http://www.crypto-world.com/FactorWorld.html}}
\end{itemize}
\end{minipage}
\vspace{12pt}

% --------------------------------------------------------------------------
As you notice the factorised compound numbers built of 2 prime factors are
much smaller than the especially structured numbers, for which primality 
tests\index{Primality testing} are able to decide whether they are prime 
or not (see chapters 2.4 and 2.5).

@@

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{The RSA procedure with actual numbers}\hypertarget{Kapitel_3_12}{}
\index{RSA}\label{rsaconcrete}

@@

% --------------------------------------------------------------------------
\subsubsection[RSA with slightly larger primes]{RSA with slightly larger primes and a text of upper case letters}
\label{rsaex2}

@@

% --------------------------------------------------------------------------
\subsubsection{RSA with even larger primes and a text made up of ASCII characters}

@@

{\bf Comments:} \\
The original message consisted of a sentence containing $31$ characters (coded
with the capital letters alphabet \index{Capital letters alphabet} from
section~\ref{rsaex2}).  Each group of $16$ decimal numbers is then combined to
form one number (the last number is filled with zeros). These numbers are
raised to the power of $e$.

@@

\bibitem[GISA2002]{GISA2002} \index{GISA 2002}
    GISA (German Information Security Agency) \\
    {\em Recommendation for key length selection}, Bonn, Sep. 2002, \\
    \href{http://www.bsi.bund.de/esig/basics/techbas/krypto/bund02v7.pdf}
    {\tt http://www.bsi.bund.de/esig/basics/techbas/krypto/bund02v7.pdf} \\
    A statement on these recommendations: \\
    \href{http://www.secorvo.de/publikat/stellungnahme-algorithmenempfehlung-020307.pdf}
    {\texttt{http://www.secorvo.de/publikat/}}\\
    \vspace*{1cm}\href{http://www.secorvo.de/publikat/stellungnahme-algorithmenempfehlung-020307.pdf}
    {\texttt{stellungnahme-algorithmenempfehlung-020307.pdf}}

@@

   \item Factorisation records and challenges \index{Factorisation!factorisation records}\\
         \href{http://www.crypto-world.com/}
         {\texttt{http://www.crypto-world.com/}} \\
         \href{http://www.crypto-world.com/FactorWorld.html}
         {\texttt{http://www.crypto-world.com/FactorWorld.html, page by Scott Contini}} \\
         \href{http://www.loria.fr/~zimmerma/records/factor.html}
         {\texttt{http://www.loria.fr/~zimmerma/records/factor.html}} \\

         \href{http://www.uni-bonn.de/Aktuelles/Pressemitteilungen/pm02/pm035-02.html}
         {\texttt{http://www.uni-bonn.de/Aktuelles/Pressemitteilungen/pm02/pm035-02.html}} \\
         \href{http://www.ercim.org/publication/Ercim\_News/enw49/franke.html, 2002-01}
         {\texttt{http://www.ercim.org/publication/Ercim\_News/enw49/franke.html, 2002-01}} \\
         \href{http://www.loria.fr/~zimmerma/records/rsa160}
         {\texttt{http://www.loria.fr/~zimmerma/records/rsa160}} \\

         \href{http://www.rsasecurity.com/rsalabs/challenges/factoring/numbers.html}
         {\texttt{http://www.rsasecurity.com/rsalabs/challenges/factoring/numbers.html}}

@@

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\newpage
\subsection*{Appendix A: the greatest common divisor (gcd) of whole numbers and the two
Algorithms of Euclid} \hypertarget{Appendix_A}{}
\addcontentsline{toc}{subsection}{Appendix A: gcd of whole numbers and the two
Algorithms of Euclid}\index{Euclidean algorithm!extended}\index{Gcd}

@@

This section list the source code of the RSA examples in
section~\ref{rsaconcrete} (``The RSA procedure with actual numbers'') using
Mathematica and Pari-GP syntax.

### 2003-05-20 script/en/chapters/primes.tex
be update numbertheory and overfull hbox fixes

Thus there is an {\em infinite} number of primes
\hyperlink{primhfk}{(Cross-reference: overview under \ref{s:primhfk} of 
the number of prime numbers in various intervals)}.\par \vskip + 10pt

>>>>

Thus there is an {\em infinite} number of primes
(Cross-reference: \hyperlink{primhfk}{overview} under \ref{s:primhfk} of 
the number of prime numbers in various intervals).\par \vskip + 10pt
